Community-based marine reserves in Mexico: do they work?

### 2018-03-20 slides/GainesLabPresentation.Rmd
Added new paths to the presentation so that it renders

# Load high-res mexican coastline
coastline_mx <- readRDS("./Data/Spatial/coastline_mx.rds")

@@

zrp <- st_read(dsn = "./Data/Spatial", layer = "ZRP", quiet = T) %>% 
  sf::st_centroid() %>% 
  select(Name, geometry) %>% 
  mutate(Type = "FR")

rescom <- st_read(dsn = "./Data/Spatial", layer = "Res_Com", quiet = T) %>% 
  sf::st_centroid() %>% 
  select(Name = Nombre, geometry) %>% 
  mutate(Type = "CB")

@@

![](./Img/Imagen5.jpg)

@@

![](./Img/plot.png)

@@

.pull-right[
![](./Img/plot.png)
]

@@

![](./Img/plot_summary.png)

@@

![](./Img/Lobsters.png)

@@

load("./Data/conapesca_2000-2015.RData")

cpi <- read.csv("./Data/CPI.csv", stringsAsFactors = F, strip.white = T)

@@

---
background-image: url(https://raw.githubusercontent.com/jcvdav/ReserveEffect/master/Img/Imagen5.jpg)
class: inverse, center, middle
background-size: cover

>>>>

# Load high-res mexican coastline
coastline_mx <- readRDS(here::here("data", "spatial","coastline_mx.rds"))

@@

zrp <- st_read(dsn = here::here("data", "spatial"), layer = "ZRP", quiet = T) %>% 
  sf::st_centroid() %>% 
  select(Name, geometry) %>% 
  mutate(Type = "FR")

rescom <- st_read(dsn = here::here("data", "spatial"), layer = "Res_Com", quiet = T) %>% 
  sf::st_centroid() %>% 
  select(Name = Nombre, geometry) %>% 
  mutate(Type = "CB")

@@

![](./img/Imagen5.jpg)

@@

![](./img/plot.png)

@@

.pull-right[
![](./img/plot.png)
]

@@

![](./img/plot_summary.png)

@@

![](./img/Lobsters.png)

@@

load(here::here("data","conapesca_2000-2015.RData"))

cpi <- read.csv(here::here("data","CPI.csv"), stringsAsFactors = F, strip.white = T)

@@

---
background-image: url(https://raw.githubusercontent.com/jcvdav/ReserveEffect/master/img/Imagen5.jpg)
class: inverse, center, middle
background-size: cover
